A Critical Appraisal of the Zero-Multiple Method: Structural, Thermodynamic, Dielectric, and Dynamical Properties of a Water System

### 2014-12-17 writedown/zm/paper.water/main.tex
backup revise

Introduction of the ZM method, formula...[ {\color{blue} COMMENT: I can
write here later}]

@@

In order to investigate the performance of ZM method, we simulate the water
system by using both SPME and ZM methods, and evaluate a set of \emph{%
benchmark quantities}. This set covers a broad range of water properties
that are of general interest. It includes the structure property (radial
distribution function), the thermodynamic properties (pressure, excess
chemical potential, constant volume/pressure heat capacity, isothermal
compressibility, thermal expansion coefficient), dielectric properties
(dielectric constant and Kirkwood-G factor) and dynamical properties
(diffusion constant and viscosity). The definitions and computing methods of
these quantities are provided in details in Appendix.~\ref%
{appendix:benchmark}. By comparing ZM to SPME, a good consistency in
computing the benchmark quantities would indicate a good accuracy of the ZM
method. More importantly, the benchmark tests provide knowledge in the
situations when the ZM method does not work so well, and help in finding the
way of tuning the working parameters to achieve higher accuracy. The ZM
method is also compared to the traditional short-range method: RF.

@@

\label{sec:protocols} In this work, we focus on a system of water molecules
modeled by TIP3P~\cite{jorgensen1983comparison} point-charge particles. 
% Other point-charge water models differ in the modeling parameters, and
The accuracy of ZM method in other water models is out of the scope of the
current work. However, since the point-charge water models share similar
idea, and only differ in the model parameters, it is highly probable that ZM
works well with other water models if it works well with TIP3P.

@@

The neighbor lists were updated every 5 time-steps. The Gromacs by default
uses the group cut-off scheme, while the ZM method recommends
an atom cut-off scheme~\cite{fukuda2011molecular,fukuda2013zero}. The difference between these cut-off
schemes is discussed in detail in e.g.~Ref.~\cite%
{hunenberger1998alternative,baumketner2009removing}. We adopted the atom
based cut-off scheme in the simulations using the SPME (short-range part)
and ZM electrostatic methods. The implementation details of the
atom cut-off scheme in Gromacs are provided in Appendix.~\ref{app:cut-off}.
The ZM method was implemented in Gromacs with the tabulated electrostatic
interaction, and the interaction tables were generated by a home-made code.

We treated the RF with the group cut-off scheme because the
group cut-off scheme is the default scheme in Gromacs. The experimental
dielectric consistency $\varepsilon _{\text{rf}}=80$ was adopted for the RF
method.
% In order to mimic the atom cut-off scheme in
% the Gromacs group cut-off implementation, the radius for neighbor list
% updating was set ${0.3}$~nm larger than the cut-off radius (the maximum of
% Coulomb cut-off and the van der Waals cut-off). 
% The \textquotedblleft 
% \texttt{group}\textquotedblright\ cut-off scheme in Gromacs was used.[ {\color{blue} COMMENT:
% Yes,..., this is not easy to understand how we mimic AC. {\color{red} it
%   should be OK as it is now.}} {\color{blue} Please see COMMENT in SecII.}]

@@

In this section we compare the benchmark quantities of the ZM method to the
SPME method to investigate the accuracy of the former. The comparison to the
RF method will also be mentioned, to show that the ZM is a promising
replacement of the RF method.

@@

\begin{sidewaystable}
  \centering
  \caption{The excess chemical potential $\mu^\exc$, constant volume molar heat capacity $C_{v,m}$, dielectric constant $\eps$, diffusion constant $D$, viscosity $\eta$, constant pressure molar heat capacity $C_{v,m}$, isothermal compressibility $\kappa_T$ and
    thermal expansion coefficient $\alpha_V$
    calculated by different methods.    
    The parentheses in the last column show the statistical uncertainty
    at the confidence level of 95~\%.
    The bold numbers indicating that its deviation from the SPME result is larger than the statistical uncertainty.
  }
  \bigskip
  \centering\small\setlength\tabcolsep{2pt}
  \begin{tabular*}{0.99\textwidth}{@{\extracolsep{\fill}}cccc cccccccc}\hline\hline
    Method      &   $r_c$ &    $l$ & $\alpha$  & $\mu^\exc$  &$C_{v,m}$ & $C_{p,m}$ &   $\kappa_T$  &$\alpha_V$ &  $\eps$ & $D$ &  $\eta$  \\
                & [nm] & & [$\textrm{nm}^{-1}$] &   [kJ/mol] &[J/(mol K)] & [J/(mol K)] & [$10^{-10}\textrm{m}^2/\textrm{N}$] &  [$10^{-3}\textrm{K}^{-1}$]&  & [$10^{-9}\textrm{m}^2/\textrm{s}$] &  [$10^{-3}\textrm{Pa}\cdot\textrm{s}$]  \\
                &    &    &    &NVT $\systemla$&NVT $\systemsb$&  NPT $\systemsb$          &  NPT $\systemsb$    &  NPT $\systemsb$    & NVT $\systemsb$& NVT $\systemsb$    & NVT $\systemsb$       \\\hline
    SPME        &1.9 & -- &2.1 & $-26.1$ (0.2) & 72.2 (1.0)  &79.2 (0.9)           & 5.94 (0.05)               &1.03 (0.02)          & 98 (3)          &         5.86  (0.07)&         0.315  (0.007)\\
    RF          &1.2 & -- &--  & $-26.0$ (0.3) & 72.3 (0.8)  &\textbf{82.3} (1.0)  & \textbf{6.51} (0.06)      &\textbf{1.15} (0.02) & \textbf{59} (1) & \textbf{6.27} (0.19)& \textbf{0.449} (0.020)\\\hline
    ZM          &1.2 & 1  &0.0 & $-26.2$ (0.3) & 71.8 (0.9)  &78.9 (1.0)           & 5.87 (0.05)               &1.01 (0.02)          & 96 (2)          & \textbf{5.53} (0.11)& \textbf{0.346} (0.006)\\ 
    ZM          &1.2 & 1  &0.5 & $-26.4$ (0.3) & 72.3 (0.8)  &78.9 (0.9)           & 5.92 (0.05)               &\textbf{1.00} (0.02) & 97 (2)          & \textbf{5.52} (0.25)& \textbf{0.339} (0.008)\\ 
    ZM          &1.2 & 1  &1.0 & $-26.0$ (0.2) & 72.4 (0.8)  &78.4 (0.9)           & 5.95 (0.05)               &1.01 (0.02)          & 96 (2)          &        {5.78} (0.25)& \textbf{0.330} (0.011)\\ 
    ZM          &1.2 & 1  &1.5 & $-26.0$ (0.2) & 71.3 (0.8)  &80.2 (0.9)           & 5.97 (0.05)               &1.04 (0.02)          & 99 (3)          & \textbf{5.71} (0.09)&        {0.312} (0.008)\\ 
    ZM          &1.2 & 1  &2.0 & $-26.1$ (0.3) & 71.3 (0.8)  &79.4 (0.9)           & \textbf{6.05} (0.05)      &1.05 (0.02)          & 96 (3)          &        {5.90} (0.04)&        {0.307} (0.007)\\\hline
    ZM          &1.2 & 2  &0.0 & $-26.2$ (0.2) & 71.5 (0.9)  &79.7 (1.0)           & 5.95 (0.05)               &1.03 (0.02)          & 95 (3)          &         5.82  (0.27)&         0.318  (0.012)\\
    ZM          &1.2 & 3  &0.0 & $-26.2$ (0.2) & 71.6 (0.9)  &79.5 (1.0)           & 5.99 (0.05)               &1.02 (0.02)          & 96 (3)          &         5.79  (0.09)&         0.321  (0.008)\\
    ZM          &1.2 & 4  &0.0 & $-26.0$ (0.3) & 71.1 (0.8)  &79.5 (1.0)           & 5.96 (0.05)               &1.03 (0.02)          &100 (2)          &         5.89  (0.09)&         0.318  (0.013)\\
    \hline\hline
  \end{tabular*}
  \label{tab:thermo}
\end{sidewaystable}

Thermodynamic quantities including, the chemical potential, constant
volume/pressure molar heat capacity, isothermal compressibility and heat
expansion coefficient, are compared in Tab.~\ref{tab:thermo}. The ZM results
are in good consistency with the SPME results. In almost all cases the
deviations from the SPME results are smaller than the statistical
uncertainty. The RF was not so bad, but the results of the constant pressure
molar heat capacity and the isothermal compressibility show considerable
errors. The dependence of the ZM results on the order\ $l$\ is little.
Although the splitting parameter, $\alpha $, also does not have significant
influence on almost all these thermodynamic quantities for $l=1$, only the
isothermal compressibility admits a weak dependence. Overall, the ZM\ agrees
with the SPME results without any bias and out-performs the RF.

@@

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/nvt.pressure.1/pressure-methods.eps}
\caption{The pressure convergence with respect to the cut-off radius. The ZM
methods with order from 1 to 4 are compared with the RF. The splitting
parameter of ZM method is set to be $\protect\alpha =0.00\,\text{nm}^{-1}$.
The black solid line indicates the magnitude of the correct pressure: 1~Bar.
The error bars present the statistical uncertainty at 95\% confidence level. 
{\color{red} This uncertainty is twice of the standard deviation of the
estimates (which are averages along MD trajectories) that is calculated by
the block average method~\protect\cite{janke2002statistical}.}
% [ {\ 
% \color{blue}It maybe good to repeat such explanation in Sec.IIIA.}].[{\ 
% \color{blue} another COMMENT: In these figures, can we see the statistical
% uncertainty of the pressure obtained by the SPME? Viz., I found no error
% bars for SPME.} {\color{red} NO SPME result is given in this figure, 1 Bar
% is the target pressure.}][{\color{blue} Can I konw the the statistical
% uncertainty of the pressure obtained by the SPME?}]
}
\label{fig:pres-comp}
\end{figure}

We investigated the dependence on the cut-off radius, $r_{\text{c}}$, on the
pressure, simulated with system $L_{0}$. The pressure calculated by ZM
method of order $l=1,2,3$ and $4$ with $\alpha =0$ \ and that by the RF
method are plotted in Fig.~\ref{fig:pres-comp}. All ZM methods converges to
the target pressure at large enough cut-off radius. Lower order ZM presents
an smaller error in the pressure calculation than the higher order ZM
method. Note ZM $l=1$ tends to under-estimate the pressure, while ZM $l=2,3$
and 4 tends to over-estimate. However, the accuracy of ZM in pressure
calculation is much higher than that of the RF method.

\begin{figure}[tbp]
\centering
\includegraphics[width=0.5\textwidth]{fig/nvt.pressure.1/pressure-l1.eps} %
% \includegraphics[width=0.24\textwidth]{fig/nvt.pressure.1/pressure-l2.eps}%
% \newline
% \includegraphics[width=0.24\textwidth]{fig/nvt.pressure.1/pressure-l3.eps} %
% \includegraphics[width=0.24\textwidth]{fig/nvt.pressure.1/pressure-l4.eps}
\caption{ The pressure convergence with respect to the cut-off radius for ZM
method $l=1$ with splitting parameter from $0.0$ to $2.0\,\text{nm}^{-1}$.
The black solid line indicates the magnitude of the correct pressure: 1~Bar.
The error bars present the statistical uncertainty at 95\% confidence level.}
\label{fig:pres-l1}
\end{figure}

The effect of $\alpha $ in the case of $l=1$ is shown in Fig.~\ref%
{fig:pres-l1}. The result of $\alpha =0.5\,$nm$^{-1}$ is similar to $\alpha
=0$ and shows good convergence. However, a higher $\alpha $ shifts the
pressure to higher side, and in particular $\alpha =2.0\,\text{nm}^{-1}$ is
too large to show no convergence to 1~Bar. This implies that $\alpha \leq 1$
should be used in the simulations where the high accuracy in the pressure is
important. This "anti-damping effect" is similarly seen in the energy
accuracy in the TIP3P model~\cite{fukuda2014zero}. 
% [JCP2014 (J. Chem. Phys. 140, 194307 (2014))].
In SI the results of the higher order are shown, which are similar to that
of $l=1$, but indicate less significant dependency on $\alpha $ for a large $%
l$\ and for a small $r_{\text{c}}$, which is consistent with the property of
the pair potential of the ZM~\cite{fukuda2014zero}. The convergence is not
sensitive to $\alpha $ up to $1.0\,\text{nm}^{-1}$.

It should be noted that even with the system $L_{0}$ that contains 13824
water molecules, the fluctuation (measured by standard deviation) of the
pressure is roughly 100~Bar, which means that it is very difficult to
achieve very accurate estimate for this quantity.  In practice a
pressure error of 20~Bar will only cause a density deviation (calculated by
the NPT simulations) of roughly 0.1\%. Taking different orders ZM method at
cut-off 1.2~nm for example, the density deviations are 0.051\%, 0.061\%,
0.097\% and 0.146\% for $l=1,2,3$ and 4, respectively. For $l\leq 3$ the
pressure error is less than 20~Bar, while for $l=4$ the pressure error is
less than 30~Bar (see Fig.~\ref{fig:pres-comp}).

% [{\color{blue} {COMMENT1:} Can we have a trajectory figure of the pressure?
% It will show that the fluctuation is large and the 10 Bar error for ZM looks
% small. If there is a suitable one, it may be good to put it in SI.} {%
% \color{red} Could you explain why? The SD should be enough for our purpose.}%
% ] [ {\color{blue} COMMENT2: Can we have some data on the (mass) density?
% Some potential users of ZM\ may worry about the deviation of the density
% from the reality due to the pressure error. I remember that the density
% error for ZM was small. It is helpful to show that the deviation of the
% density is sufficiently small. These two comments indicates that one wants
% to feel how good or bad about the 10 Bar error.} {\color{red} Done}][ {%
% \color{blue} Thank you very much for your consideration of the density. {%
% COMMENT1: please see my question in the last page. COMMENT2: The deviation
% of the pressure between the ZM and PME should be due to this density
% deviation between the ZM and PME (0.1\%). Namely {0.1\% density deviation
% should cause 10 atm deviation.}\ How about this confirmation? ---The
% pressure by ZM\ in figs1\&2 was calculated with the NTV MD where the cell
% size was determined by the \textit{PME} NTP. So, if we will do NTV MD with
% the cell size determined by the \textit{ZM} NTP (which was used to calculate
% the current density), and if we calculate the pressure by ZM with this new
% NTV, then we should have 1 atm pressure for may cutoff lengths. If this is
% true, then we can show that the 10 atm deviation from the PME is not the
% serious problem but a tiny density deviation issue.--- How about this idea? }%
% }]

% \begin{table}
%   \centering
%   \caption{A list of the dielectric constant calculated for different systems by different methods.
%     The parameters are provided. The parenthesises in the last column show the statistical uncertainty
%     of the last two digits up to the confidence level of 95~\%.}
%   \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}cccc rr}\hline\hline
%     System & Method      &       $\alpha$ [$\textrm{nm}^{-1}$] & $r_c$ [nm] &    $l$     &       $\eps$ \\\hline
%     $\systemmb$  &       ZM          &       0.00    &       1.2     &       1       &       99.8 (3.8)\\ 
%     $\systemmb$  &       ZM          &       0.00    &       1.2     &       2       &       95.2 (3.6)\\ 
%     $\systemmb$  &       ZM          &       0.00    &       1.2     &       3       &       93.9 (3.7)\\ 
%     $\systemmb$  &       ZM          &       0.00    &       1.5     &       3       &       98.7 (3.8)\\ 
%     $\systemmb$  &       ZM          &       0.00    &       1.8     &       3       &      100.7 (3.6)\\ 
%     $\systemmb$  &       ZM          &       0.00    &       1.2     &       4       &       94.7 (3.6)\\
%     $\systemmb$   & SPME          & 2.09  & 1.9   &       --      &       98.8 (4.0) \\
%     $\systemmb$  & RF             & --  & 1.2 & -- & 60.6   (1.7) \\
%     $\systemlb$  &       ZM          &       0.00    &       1.2     &       1       &       97.1 (3.2)\\ 
%     $\systemlb$  &       ZM          &       0.00    &       1.2     &       2       &       95.6 (3.5)\\ 
%     $\systemlb$  &       ZM          &       0.00    &       1.2     &       3       &       95.8 (4.6)\\ 
%     $\systemlb$  &       ZM          &       0.00    &       1.5     &       3       &       98.0 (3.3)\\ 
%     $\systemlb$  &       ZM          &       0.00    &       1.8     &       3       &       98.9 (4.2)\\ 
%     $\systemlb$  &       ZM          &       0.00    &       2.1     &       3       &       98.8 (3.9)\\ 
%     $\systemlb$  &       ZM          &       0.00    &       1.2     &       4       &       97.8 (3.9)\\
%    $\systemlb$   & SPME          & 2.09  & 1.9   &       --      &       98.7 (3.5) \\
%     $\systemlb$  & RF             & --  & 1.2 & -- & 60.8   (2.0) \\
%     \hline\hline
%   \end{tabular*}
%   \label{tab:tmp2}
% \end{table}

@@

\begin{figure}[tbp]
\centering
\includegraphics[width=0.5\textwidth]{fig/result.nvt.tiny/fig-eps-t-3000.eps}
\caption{The dielectric constant convergence with respect to length of the
trajectories used to compute the value. The SPME, ZM method $l=1$ to 4 and
RF are presented. The cut-off distance of ZM and RF methods was 1.2~nm. The
working parameters of SPME are given in Sec.~\protect\ref{sec:protocols} The
system used for simulation is $S_{1}$.}
\label{fig:eps-conv}
\end{figure}

The dielectric constant computed by ZM method at different orders are listed
in Tab.~\ref{tab:thermo}, and are consistent with the SPME computed results.
In contrast, the RF method has poor accuracy in the dielectric constant. It
is well known that the dielectric feature shows system-size dependence~\cite%
{vanderSpoel2006origin}, therefore we further investigated this dependence
and also the effect of the cutoff length, as shown in Table~I of SI. ZM
shows good results without any system-size dependency and indicate $r_{\text{%
c}}\sim 1.2\,$nm\ being suffice for the accuracy. Since a slow convergence
is also known for the dielectric constant, we have monitored the behavior as
shown in Fig.~\ref{fig:eps-conv}, and confirm the sufficient convergence
w.r.t.~the length of the trajectories.

>>>>

Introduction of the ZMM, formula...[ {\color{blue} COMMENT: I can
write here later}]

@@

In order to investigate the physical-chemical properties obtained  by ZMM, we simulate the water
system by using both SPME and ZMM, and evaluate a set of \emph{%
benchmark quantities}. This set covers a broad range of water properties
that are of general interest. It includes the structure property (radial
distribution function), the thermodynamic properties (pressure, excess
chemical potential, constant volume/pressure heat capacity, isothermal
compressibility, thermal expansion coefficient), dielectric properties
(dielectric constant and Kirkwood-G factor) and dynamical properties
(diffusion constant and viscosity). The definitions and computing methods of
these quantities are provided in details in Appendix.~\ref%
{appendix:benchmark}. By comparing ZMM to SPME, a good consistency in
computing the benchmark quantities should indicate a good accuracy of the ZMM.
More importantly, the benchmark tests provide knowledge in the
situations when the ZMM does not work so well, and help in finding the
way of tuning the working parameters to achieve higher accuracy. The ZMM
is also compared to the traditional short-range method: RF.

@@

\label{sec:protocols} In this work, we focus on a system of water molecules
modeled by TIP3P~\cite{jorgensen1983comparison} point-charge particles. 
% Other point-charge water models differ in the modeling parameters, and
The accuracy of ZMM in other water models is out of the scope of the
current work. However, since the point-charge water models share similar
idea, and only differ in the model parameters, it is highly probable that ZMM
works well with other water models if it works well with TIP3P.

@@

The neighbor lists were updated every 5 time-steps. The Gromacs by default
uses the group cut-off scheme, while the ZMM recommends
an atom cut-off scheme~\cite{fukuda2011molecular,fukuda2013zero}. The difference between these cut-off
schemes is discussed in detail in e.g.~Ref.~\cite%
{hunenberger1998alternative,baumketner2009removing}. We adopted the atom
based cut-off scheme in the simulations using the SPME (short-range part)
and ZMM electrostatic. The implementation details of the
atom cut-off scheme in Gromacs are provided in Appendix.~\ref{app:cut-off}.
The ZMM was implemented in Gromacs with the tabulated electrostatic
interaction, and the interaction tables were generated by a home-made code.

We treated the RF with the group cut-off scheme because the
group cut-off scheme is the default scheme in Gromacs. The experimental
dielectric consistency $\varepsilon _{\text{rf}}=80$ was adopted for the RF.
% In order to mimic the atom cut-off scheme in
% the Gromacs group cut-off implementation, the radius for neighbor list
% updating was set ${0.3}$~nm larger than the cut-off radius (the maximum of
% Coulomb cut-off and the van der Waals cut-off). 
% The \textquotedblleft 
% \texttt{group}\textquotedblright\ cut-off scheme in Gromacs was used.[ {\color{blue} COMMENT:
% Yes,..., this is not easy to understand how we mimic AC. {\color{red} it
%   should be OK as it is now.}} {\color{blue} Please see COMMENT in SecII.}]

@@

In this section we compare the benchmark quantities of the ZMM to the
SPME method to investigate the accuracy of the former. The comparison to the
RF  is also mentioned, to show that the ZMM could be a promising
replacement of the RF.

@@

\begin{sidewaystable}
  \centering
  \caption{The excess chemical potential $\mu^\exc$, constant volume molar heat capacity $C_{v,m}$, dielectric constant $\eps$, diffusion constant $D$, viscosity $\eta$, constant pressure molar heat capacity $C_{v,m}$, isothermal compressibility $\kappa_T$ and
    thermal expansion coefficient $\alpha_V$
    calculated by different methods.    
    The parentheses in the last column show the statistical uncertainty
    at the confidence level of 95~\%.
    The bold numbers indicating that its deviation from the SPME result is larger than the statistical uncertainty.
  }
  \bigskip
  \centering\small\setlength\tabcolsep{2pt}
  \begin{tabular*}{0.99\textwidth}{@{\extracolsep{\fill}}cccc cccccccc}\hline\hline
    Method      &   $r_c$ &    $l$ & $\alpha$  & $\mu^\exc$  &$C_{v,m}$ & $C_{p,m}$ &   $\kappa_T$  &$\alpha_V$ &  $\eps$ & $D$ &  $\eta$  \\
                & [nm] & & [$\textrm{nm}^{-1}$] &   [kJ/mol] &[J/(mol K)] & [J/(mol K)] & [$10^{-10}\textrm{m}^2/\textrm{N}$] &  [$10^{-3}\textrm{K}^{-1}$]&  & [$10^{-9}\textrm{m}^2/\textrm{s}$] &  [$10^{-3}\textrm{Pa}\cdot\textrm{s}$]  \\
                &    &    &    &NVT $\systemla$&NVT $\systemsb$&  NPT $\systemsb$          &  NPT $\systemsb$    &  NPT $\systemsb$    & NVT $\systemsb$& NVT $\systemsb$    & NVT $\systemsb$       \\\hline
    SPME        &1.9 & -- &2.1 & $-26.1$ (0.2) & 72.2 (1.0)  &79.2 (0.9)           & 5.94 (0.05)               &1.03 (0.02)          & 98 (3)          &         5.86  (0.07)&         0.315  (0.007)\\
    RF          &1.2 & -- &--  & $-26.0$ (0.3) & 72.3 (0.8)  &\textbf{82.3} (1.0)  & \textbf{6.51} (0.06)      &\textbf{1.15} (0.02) & \textbf{59} (1) & \textbf{6.27} (0.19)& \textbf{0.449} (0.020)\\\hline
    ZMM          &1.2 & 1  &0.0 & $-26.2$ (0.3) & 71.8 (0.9)  &78.9 (1.0)           & 5.87 (0.05)               &1.01 (0.02)          & 96 (2)          & \textbf{5.53} (0.11)& \textbf{0.346} (0.006)\\ 
    ZMM          &1.2 & 1  &0.5 & $-26.4$ (0.3) & 72.3 (0.8)  &78.9 (0.9)           & 5.92 (0.05)               &\textbf{1.00} (0.02) & 97 (2)          & \textbf{5.52} (0.25)& \textbf{0.339} (0.008)\\ 
    ZMM          &1.2 & 1  &1.0 & $-26.0$ (0.2) & 72.4 (0.8)  &78.4 (0.9)           & 5.95 (0.05)               &1.01 (0.02)          & 96 (2)          &        {5.78} (0.25)& \textbf{0.330} (0.011)\\ 
    ZMM          &1.2 & 1  &1.5 & $-26.0$ (0.2) & 71.3 (0.8)  &80.2 (0.9)           & 5.97 (0.05)               &1.04 (0.02)          & 99 (3)          & \textbf{5.71} (0.09)&        {0.312} (0.008)\\ 
    ZMM          &1.2 & 1  &2.0 & $-26.1$ (0.3) & 71.3 (0.8)  &79.4 (0.9)           & \textbf{6.05} (0.05)      &1.05 (0.02)          & 96 (3)          &        {5.90} (0.04)&        {0.307} (0.007)\\\hline
    ZMM          &1.2 & 2  &0.0 & $-26.2$ (0.2) & 71.5 (0.9)  &79.7 (1.0)           & 5.95 (0.05)               &1.03 (0.02)          & 95 (3)          &         5.82  (0.27)&         0.318  (0.012)\\
    ZMM          &1.2 & 3  &0.0 & $-26.2$ (0.2) & 71.6 (0.9)  &79.5 (1.0)           & 5.99 (0.05)               &1.02 (0.02)          & 96 (3)          &         5.79  (0.09)&         0.321  (0.008)\\
    ZMM          &1.2 & 4  &0.0 & $-26.0$ (0.3) & 71.1 (0.8)  &79.5 (1.0)           & 5.96 (0.05)               &1.03 (0.02)          &100 (2)          &         5.89  (0.09)&         0.318  (0.013)\\
    \hline\hline
  \end{tabular*}
  \label{tab:thermo}
\end{sidewaystable}

Thermodynamic quantities including, the chemical potential, constant
volume/pressure molar heat capacity, isothermal compressibility and heat
expansion coefficient, are compared in Tab.~\ref{tab:thermo}. The ZMM results
are in good consistency with the SPME results. In almost all cases the
deviations from the SPME results are smaller than the statistical
uncertainty. The RF was not so bad, but the results of the constant pressure
molar heat capacity and the isothermal compressibility show considerable
errors. The dependence of the ZMM results on the order\ $l$\ is little.
Although the splitting parameter, $\alpha $, also does not have significant
influence on almost all these thermodynamic quantities for $l=1$, only the
isothermal compressibility admits a weak dependence. Overall, the ZMM\ agrees
with the SPME results without any bias and out-performs the RF.

@@

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/nvt.pressure.1/pressure-methods.eps}
\caption{The pressure convergence with respect to the cut-off radius. The ZMM
  with order from 1 to 4 are compared with the RF. The splitting
parameter of ZMM  is set to be $\protect\alpha =0.00\,\text{nm}^{-1}$.
The black solid line indicates the magnitude of the correct pressure: 1~Bar.
The error bars present the statistical uncertainty at 95\% confidence level. 
{\color{red} This uncertainty is twice of the standard deviation of the
estimates (which are averages along MD trajectories) that is calculated by
the block average method~\protect\cite{janke2002statistical}.}
% [ {\ 
% \color{blue}It maybe good to repeat such explanation in Sec.IIIA.}].[{\ 
% \color{blue} another COMMENT: In these figures, can we see the statistical
% uncertainty of the pressure obtained by the SPME? Viz., I found no error
% bars for SPME.} {\color{red} NO SPME result is given in this figure, 1 Bar
% is the target pressure.}][{\color{blue} Can I konw the the statistical
% uncertainty of the pressure obtained by the SPME?}]
}
\label{fig:pres-comp}
\end{figure}

We investigated the dependence on the cut-off radius, $r_{\text{c}}$, on the
pressure, simulated with system $L_{0}$. The pressure calculated by ZMM
of order $l=1,2,3$ and $4$ with $\alpha =0$ \ and that by the RF
are plotted in Fig.~\ref{fig:pres-comp}. All ZMM  converges to
the target pressure at large enough cut-off radius. Lower order ZMM presents
an smaller error in the pressure calculation than the higher order ZMM.
Note ZMM $l=1$ tends to under-estimate the pressure, while ZMM $l=2,3$
and 4 tends to over-estimate. However, the accuracy of ZMM in pressure
calculation is much higher than that of the RF.

\begin{figure}[tbp]
\centering
\includegraphics[width=0.5\textwidth]{fig/nvt.pressure.1/pressure-l1.eps} %
% \includegraphics[width=0.24\textwidth]{fig/nvt.pressure.1/pressure-l2.eps}%
% \newline
% \includegraphics[width=0.24\textwidth]{fig/nvt.pressure.1/pressure-l3.eps} %
% \includegraphics[width=0.24\textwidth]{fig/nvt.pressure.1/pressure-l4.eps}
\caption{ The pressure convergence with respect to the cut-off radius for ZMM
  $l=1$ with splitting parameter from $0.0$ to $2.0\,\text{nm}^{-1}$.
The black solid line indicates the magnitude of the correct pressure: 1~Bar.
The error bars present the statistical uncertainty at 95\% confidence level.}
\label{fig:pres-l1}
\end{figure}

The effect of $\alpha $ in the case of $l=1$ is shown in Fig.~\ref%
{fig:pres-l1}. The result of $\alpha =0.5\,$nm$^{-1}$ is similar to $\alpha
=0$ and shows good convergence. However, a higher $\alpha $ shifts the
pressure to higher side, and in particular $\alpha =2.0\,\text{nm}^{-1}$ is
too large to show no convergence to 1~Bar. This implies that $\alpha \leq 1\,\text{nm}^{-1}$
should be used in the simulations where the high accuracy in the pressure is
important. This "anti-damping effect" is similarly seen in the energy
accuracy in the TIP3P model~\cite{fukuda2014zero}. 
% [JCP2014 (J. Chem. Phys. 140, 194307 (2014))].
In SI the results of the higher order are shown, which are similar to that
of $l=1$, but indicate less significant dependency on $\alpha $ for a large $%
l$\ and for a small $r_{\text{c}}$, which is consistent with the property of
the pair potential of the ZMM~\cite{fukuda2014zero}. The convergence is not
sensitive to $\alpha $ up to $1.0\,\text{nm}^{-1}$.

It should be noted that even with the system $L_{0}$ that contains 13824
water molecules, the fluctuation (measured by standard deviation) of the
pressure is roughly 100~Bar, which means that it is very difficult to
achieve very accurate estimate for this quantity.  In practice a
pressure error of 20~Bar will only cause a density deviation (calculated by
the NPT simulations) of roughly 0.1\%. Taking different orders ZMM  at
cut-off 1.2~nm for example, the density deviations are 0.051\%, 0.061\%,
0.097\% and 0.146\% for $l=1,2,3$ and 4, respectively. For $l\leq 3$ the
pressure error is less than 20~Bar, while for $l=4$ the pressure error is
less than 30~Bar (see Fig.~\ref{fig:pres-comp}).

% [{\color{blue} {COMMENT1:} Can we have a trajectory figure of the pressure?
% It will show that the fluctuation is large and the 10 Bar error for ZMM looks
% small. If there is a suitable one, it may be good to put it in SI.} {%
% \color{red} Could you explain why? The SD should be enough for our purpose.}%
% ] [ {\color{blue} COMMENT2: Can we have some data on the (mass) density?
% Some potential users of ZMM\ may worry about the deviation of the density
% from the reality due to the pressure error. I remember that the density
% error for ZMM was small. It is helpful to show that the deviation of the
% density is sufficiently small. These two comments indicates that one wants
% to feel how good or bad about the 10 Bar error.} {\color{red} Done}][ {%
% \color{blue} Thank you very much for your consideration of the density. {%
% COMMENT1: please see my question in the last page. COMMENT2: The deviation
% of the pressure between the ZMM and PME should be due to this density
% deviation between the ZMM and PME (0.1\%). Namely {0.1\% density deviation
% should cause 10 atm deviation.}\ How about this confirmation? ---The
% pressure by ZMM\ in figs1\&2 was calculated with the NTV MD where the cell
% size was determined by the \textit{PME} NTP. So, if we will do NTV MD with
% the cell size determined by the \textit{ZMM} NTP (which was used to calculate
% the current density), and if we calculate the pressure by ZMM with this new
% NTV, then we should have 1 atm pressure for may cutoff lengths. If this is
% true, then we can show that the 10 atm deviation from the PME is not the
% serious problem but a tiny density deviation issue.--- How about this idea? }%
% }]

% \begin{table}
%   \centering
%   \caption{A list of the dielectric constant calculated for different systems by different methods.
%     The parameters are provided. The parenthesises in the last column show the statistical uncertainty
%     of the last two digits up to the confidence level of 95~\%.}
%   \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}cccc rr}\hline\hline
%     System & Method      &       $\alpha$ [$\textrm{nm}^{-1}$] & $r_c$ [nm] &    $l$     &       $\eps$ \\\hline
%     $\systemmb$  &       ZMM          &       0.00    &       1.2     &       1       &       99.8 (3.8)\\ 
%     $\systemmb$  &       ZMM          &       0.00    &       1.2     &       2       &       95.2 (3.6)\\ 
%     $\systemmb$  &       ZMM          &       0.00    &       1.2     &       3       &       93.9 (3.7)\\ 
%     $\systemmb$  &       ZMM          &       0.00    &       1.5     &       3       &       98.7 (3.8)\\ 
%     $\systemmb$  &       ZMM          &       0.00    &       1.8     &       3       &      100.7 (3.6)\\ 
%     $\systemmb$  &       ZMM          &       0.00    &       1.2     &       4       &       94.7 (3.6)\\
%     $\systemmb$   & SPME          & 2.09  & 1.9   &       --      &       98.8 (4.0) \\
%     $\systemmb$  & RF             & --  & 1.2 & -- & 60.6   (1.7) \\
%     $\systemlb$  &       ZMM          &       0.00    &       1.2     &       1       &       97.1 (3.2)\\ 
%     $\systemlb$  &       ZMM          &       0.00    &       1.2     &       2       &       95.6 (3.5)\\ 
%     $\systemlb$  &       ZMM          &       0.00    &       1.2     &       3       &       95.8 (4.6)\\ 
%     $\systemlb$  &       ZMM          &       0.00    &       1.5     &       3       &       98.0 (3.3)\\ 
%     $\systemlb$  &       ZMM          &       0.00    &       1.8     &       3       &       98.9 (4.2)\\ 
%     $\systemlb$  &       ZMM          &       0.00    &       2.1     &       3       &       98.8 (3.9)\\ 
%     $\systemlb$  &       ZMM          &       0.00    &       1.2     &       4       &       97.8 (3.9)\\
%    $\systemlb$   & SPME          & 2.09  & 1.9   &       --      &       98.7 (3.5) \\
%     $\systemlb$  & RF             & --  & 1.2 & -- & 60.8   (2.0) \\
%     \hline\hline
%   \end{tabular*}
%   \label{tab:tmp2}
% \end{table}

@@

\begin{figure}[tbp]
\centering
\includegraphics[width=0.5\textwidth]{fig/result.nvt.tiny/fig-eps-t-3000.eps}
\caption{The dielectric constant convergence with respect to length of the
trajectories used to compute the value. The SPME, ZMM  $l=1$ to 4 and
RF are presented. The cut-off distance of ZMM and RF  was 1.2~nm. The
working parameters of SPME are given in Sec.~\protect\ref{sec:protocols} The
system used for simulation is $S_{1}$.}
\label{fig:eps-conv}
\end{figure}

The dielectric constant computed by ZMM  at different orders are listed
in Tab.~\ref{tab:thermo}, and are consistent with the SPME computed results.
In contrast, the RF  has poor accuracy in the dielectric constant. It
is well known that the dielectric feature shows system-size dependence~\cite%
{vanderSpoel2006origin}, therefore we further investigated this dependence
and also the effect of the cutoff length, as shown in Table~I of SI. ZMM
shows good results without any system-size dependency and indicate $r_{\text{%
c}}\sim 1.2\,$nm\ being suffice for the accuracy. Since a slow convergence
is also known for the dielectric constant, we have monitored the behavior as
shown in Fig.~\ref{fig:eps-conv}, and confirm the sufficient convergence
w.r.t.~the length of the trajectories.
